asc_file_database

### 2019-03-11 src/stack_test.Rmd
looping model and plot predictions (note some files coming as empty .png)

# now loop to create stacks
unlayer <- read.csv("../data/env/asc_layerlist.csv", header = TRUE)
unlayer[] <- lapply(unlayer, as.character) #from https://stackoverflow.com/questions/2851015/convert-data-frame-columns-from-factors-to-characters
aea <- raster("../output/env/aea.tif")

@@

}
dev.off() # stops automatic saving of the plot to a png
# now call the stack...
{
stack <- stackOpen("st19920310.stk")
}
```

>>>>

# now loop to create stacks
janpres <- read.csv("../output/bio/maxenttestjanpr.csv", header = TRUE)
janpres$occ <- 1
janab <- read.csv("../output/bio/maxenttestjanab.csv", header = TRUE)
janab$occ <- 0
prab <- rbind(janpres, janab)
prab$originalscientificname <- "cap" #because species name needs to be the same
pa <- prab$occ
prab <- subset(prab, select = -c(x, y, occ, originalscientificname)) #ok so for maxent in r just need the variables
prab

unlayer <- read.csv("../data/env/asc_layerlist1998.csv", header = TRUE)
unlayer <- subset(unlayer, ascmonths == 1)
unlayer <- unlayer[-c(1), ]
unlayer[] <- lapply(unlayer, as.character) #from https://stackoverflow.com/questions/2851015/convert-data-frame-columns-from-factors-to-characters
aea <- raster("../output/env/aea.tif")

@@

}
dev.off() # stops automatic saving of the plot to a png
# now call the stack...
